A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
clearly introduce functions as belonging to the beading strategy

What constitutes an optimal distribution is governed by a beading strategy.
Our framework allows for different beading strategies which can optimize for different criteria.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into approximately equidistant segments.
See \cref{discretization} and \cref{shape_decomp_complex}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical represenatation of the medial axis; see \cref{mat_3d}.

@@

\subsection{Beading}
We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which intuitively look like `the center' of the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the skeleton.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
See \cref{distance_based_angles}.
This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of significant regions.

@@

\subsubsection{Bead counts}
In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
(The feature diameter is twice the radius.)
We might choose different functions for $b$ depending on the beading strategy used.

>>>>

What constitutes an optimal distribution is governed by a beading strategy.
Our framework allows for different beading strategies which can optimize for different criteria.
A beading strategy is defined by several several functions which govern the behavior of our framework.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and \cref{shape_decomp_complex}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical represenatation of the medial axis; see \cref{mat_3d}.

@@

\subsection{Bead counts}
We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which arew in some sense \emph{central} to the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the skeleton.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
See \cref{distance_based_angles}.
This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of significant regions.
See \cref{discretization}.

@@

\subsubsection{Initial bead count}
In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
(The feature diameter is twice the radius.)
The function $b$ is determined by the beading strategy.
